Case Study: 16S microbiome data (Schubert et al., 2014)

### 2018-02-20 datasets/microbiome/microbiome-schubert.Rmd
Add Goodrich analysis; fix errors in filtering of other data sets

## Remove OTUs w/ <= min reads, samples w/ <= min reads
otu <- otu[, colSums(otu) > min_otu]
otu <- otu[rowSums(otu) > min_sample, ]

@@

```{r, schubert-sb, results="hide", message=FALSE, eval=TRUE}
for (nmids in c(5, 50, 150)) {
    print(nmids)
    bd <- initializeBenchDesign(nmids = nmids)
    ## remove ASH from comparison
    bd <- dropBMethod(bd, "ashs")

>>>>

## Remove OTUs w/ <= min reads, samples w/ <= min reads
otu <- otu[rowSums(otu) > min_otu, ]
otu <- otu[, colSums(otu) > min_sample]

@@

```{r, schubert-sb, results="hide", message=FALSE, eval=TRUE}
for (nmids in c(5, 50, 150)) {
    ## use common BenchDesign w/out ASH
    bd <- initializeBenchDesign(nmids = nmids)
    bd <- dropBMethod(bd, "ashs")
